Towards Bringing Together Numerical Methods for Partial Differential Equation and Deep Neural Networks

### 2020-03-03 paper/eccv2020submission.tex
Writing out a part of the methodology section of the paper

The models were trained with real simulation data. We first descibe the process of generating said data, then we give details on the training procedure and the architecture of the models. We then descibe the three types of models that we build and evaluated.

\subsection{Simulation Setup}
\begin{itemize}
\item first describe the simulation setup in details
\item initial conditions and boundary conditions --- inflow condition, no slip conditions, outflow condition
\item schematic of the channel with the object in it
\item the simulations were preformed by a FEM solver --- HiFlow. The final images were rendered by ParaView. The images were cropped in order to contain only the relevant region of the simulation.
\item Gray scale images because [\ldots]
\item Example images
\item The parameters of the simulation were appropriately chosen. Argumentation with the Reynold's number. We want interesting effects but not a turbulent flow.
\item Simulations according to the Navier-Stokes equations are appropriate only if the flow is laminar. 
\item Concrete parameter numbers [\ldots]
\item Details on how HiFlow runs the simulation --- method, parameters, timestep time.
\end{itemize}

\subsection{Networks Details}

@@

% LocalWords:  Convolutional timestep timesteps

>>>>

\emph{The models were trained with real simulation data. We first describe the process of generating said data, then we give details on the training procedure and the architecture of the models. We then descibe the three types of models that we build and evaluated.}

\subsection{Simulation Setup}
The training data was generated by performing numerous simulations of an incompressible fluid flow around a rectangular object in a channel. The simulations were modeled according to the Navier-Stokes equations for incompressible flow. Because we are interested in the image representations of the simulations, we are dealing only with the 2D case. There are several boundary conditions that describe the simulation setup:
\begin{itemize}
\item Inflow condition on the left side of the channel
\item Outflow condition on the right side of the channel
\item No slip condition on bottom and top side of the channel as well as the sides of the object.
\end{itemize}
The simulation setup has three separate adjustable parameters --- inflow speed, fluid density and fluid viscosity.
\\
We generated three sets of simulations for training the three kinds of models.
\begin{itemize}
\item plain: a single simulation with \ldots.
\item varying inflow speed: \ldots simulations with different inflow speed. The inflow speeds are in the range of \ldots with a step of \ldots.
\item varying viscosity and density of the fluid: \ldots simulations all with different fluid viscosity and density. The viscosity was in the range of \ldots with a step of \ldots and the density was in the range of \ldots with a step of \ldots. We used the product of the two parameter ranges to perform simulations with all of the possible combinations between the two parameters.
\end{itemize}

The choice of the concrete values for the parameters was deliberate. All of the values are chosen so that the Reynolds number of the simulations in the range of \ldots. This keeps the flow laminar while still making it interesting enough. We were interested whether the built models can predict the emerging Kármán vortex street behind the object in the channel. Thus the Reynolds numbers were chosen so that the effect can occur.

The simulations were performed numerically by solving the differential equation describing the flow --- the Navier-Stokes equation. This was done with a numerical solver --- HiFlow ---  that works on base of Finite element method. The solver supports parallelization with MPI and OpenMP and we used 12 MPI processes to run each simulation. For all of the simulations the timestep for of solver was set to $0.035$ seconds. This means the a single timestep of the simulations corresponds to a $0.035$ seconds of physical time.

The numerical solver on itself cannot be used to render the simulation results to images. For this reason we used ParaView to load the simulation data and exported it as a sequence of images in PNG format. We opted out for using grayscale images as early experiments with RGB-images did not deliver satisfying results. We used the default ``Grayscale'' color preset of ParaView to visualize the results.

\subsection{Network Details}
\emph{In this subsection we turn our attention to the details around the architecture of the used network.}

The architecture of the used network and the training approach are entirely based on pix2pix.

@@

% LocalWords:  Convolutional timestep timesteps grayscale
